\chapter{Project Summary}\label{ch:project-summary}

\selectlanguage{english}

Setipp is a French company, based in Tours, offering telecommunications, isolated worker safety and professional geolocation/fleet management solutions under the brand names Setipp, Beepiz and SuiviDeFlotte.net respectively.

It is within this company that I had the chance to do my work-study training program year to prepare myself for the degree of Application designer and developer.

At the company, I joined the SuiviDeFlotte.net geolocation web development team. My tutor and I, along with a colleague who joined us later, we worked on a completely new project, an API, called ``Document Pipeline.'' The purpose of the API was to process various types of documents coming from other services of the company, such as text files containing fuel purchase transactions or scanned invoices. It needed to extract and store the data from these documents in the database. The API had to be designed in a way that it could easily be expanded to handle processing of new file types in the future.

We developed the API using the Laravel framework and stored the data in several MariaDB databases. During the project, I also worked on transforming the web user interface for uploading files containing fuel purchase transactions within the geolocation/fleet management website, another Laravel project, to adapt its functionality to the new API. This interface utilized the Blade templating language and the Vue.js framework.

Within the geolocation development team, we followed agile principles, specifically applying the SCRUM methodology to organize our work, which allowed us to adapt flexibly to emerging needs.