\chapter{Project Summary}\label{ch:project-summary}

\selectlanguage{english}

My name is Csaba SCHNITCHEN, I'm 46 years old. With a degree in biology/ecology from Hungary and a Ph.D. in environmental sciences, I worked as a lecturer and researcher until 2020. During my ecological research, I gained programming experience using R and Python for creating ecological models and figures.

In 2020, I moved to France and decided to pursue a career in computer science. In 2022, I completed the web and mobile development training, followed by application design and development studies at CEFIM. As part of my training, I interned at Setipp, a company offering telecommunications, remote worker safety, and fleet management solutions under the brand names Setipp, Beepiz, and SuiviDeFlotte respectively.

At the company, I joined the SuiviDeFlotte web development team and worked on a new module called \foreignquote{french}{Document Pipeline}. This API processed various documents, extracting and storing data from files like fuel purchase transactions and invoices. The module, built with Laravel and using MariaDB, was designed for future expansion to handle additional file types.

Furthermore, I enhanced the web user interface for uploading fuel purchase transaction files in the fleet management website. The interface was developed using Blade templating language and Vue.js framework.

In our agile web development team, we followed the SCRUM methodology, enabling us to adapt flexibly to evolving requirements.